foreground detection via Deep Variation Transformation

### 2018-08-25 draft.tex
.

% XXX there is no such command of authorruning!!!!!!
% XXX 根本就没有authorruning 命令！！！
% \authorrunning{Lecture Notes in Computer Science: Chongqing University}

@@

\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyze the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we analyze the variation of pixel observations, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
A fully convolutional network(FCN) is applied to find a transformation for pixel variations, which guarantees the linear separability of transformed pixels.
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
In particular,
the pixel variation is represented by the sequence of pixel observations and used as the input of the FCN.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a liner classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Benefied from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
the proposed approach adaptively generate superior peroformances in diversly complex scenes.
%
Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
%
\end{abstract}

@@

%具体介绍
% XXX 一句话，换一行！！！
% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for foreground detection in diversely natural scenes. 
In the DVTL model, 
the sequence of pixel observations is used to represent the variation and input into the network for learning,
which encode both the intensity distribution and sequential information.
%
Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of transformed pixel variation generated by mapping in a new space.
%
In particular,
we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
%
Benefited from the strong learning ability of FCN,
proposed approach works well in diversely complex scenes adaptively.
%
%Moreover,
%since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
% 
% 
% 
% \todo{This paragraph is too short! provide comprehensive details of our work!}
% % The final prediction can be obtained by thresholding of the transformed variation. 
% %Our contributions can be summarized as follows:
% The contridbutions of proposed approach are shown as follows:
% \begin{itemize}
% \item We proposed the pixel observation matrix to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
%     The observation matrix is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
% \item We propose a deep neural network for variation transformation. 
%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
% \end{itemize}
% 
%文章结构

%The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. 
% XXX 不会用引用可以问我或者曲师兄。
The reset part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
%
The details of the variation transformation are presented in \refsec{sec3}. The proposed fully convolutional network is illustrated in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}. 
% \todo{please revise this part by using command refsec}

\section{Related Work}
\label{sec2}
% XXX 引用文章的方式，Bouwmans2014 在ref.bib文件里,不懂去问曲师兄！！！！
%\cite{Bouwmans2014}
% Ren:删去了冗余的一句话。
Over the last few decades, a huge number of background modeling methods have been proposed,
which are broadly categorized into pixel-based, region-based and learning-based methods.
\subsection{pixel-based methods}
% Ren:重新解释了pixel based methods
Pixel-based methods usually assume the independence between neighboring pxiels,
and utilize the low-level features, such as color or gradients for background subtraction.
% cqzhao:这两句连接性不强
% Pixel-based methods assume that pixels are independent to each other and have no consideration of the spatial association with neighboring pixels. 
% Based on low-level features, such as color and gradients, pixel-based methods are computationally efficient and easy to deploy.

%GMM 
% Ren:这里你说over time 不专业，但是论文里用得挺多的啊，表示随时间推移。还有那一句 pixels are .... to be if there exists ....， 我也是在其他论文里借过来用的。i
% 原文是Incoming pixels from video frames are labeled as background if there exists a Gaussian in the GMM, where the distance between its mean and the pixel lies within a certain bound. 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
% 注意英语和汉语的表达习惯
% The most popular pixels-based methods are Gaussian Mixture Model (GMM) methods\cite{Stauffer1999}, 
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
%over time. 
Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
%GMM+i
Moreover,
Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
% Ren: 这里你说看不懂，我的意思是想说，GMM+里面参数会自动更新。并且每一个像素位置的高斯个数也会自适应调整。原文里说的是： Recursive equations are used to constantly update the parameters and but also to simultaneously select the appropriate number of components for each pixel.
% An improved GMM method is introduced by Zivkovic\cite{Zivkovic2004} with the utilization of recursive equations, 
% which can 
% automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
%Another popular algorithm in pixel based category is based on the Codebook. 
%Ren: 干脆删掉这一句了。。。
%Ren: 下面也重新写了。
Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lies within a certain bound.

%KDE
% Ren这里确实没写好，因为有点看不太明白KDE.
A non-parametric background model is proposed in \cite{Elgammal2000Non}. 
Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
%Vibe
% Ren: 关于这个Another我觉得没问题啊，因为之前一句是讲非参数的方法KDE,这里说另一个非参数的方法我觉得没毛病啊。
% Ren: 还有 when there exists 这个短语确实没毛病啊，搜谷歌学术里这么用的也很多啊。
Another non-parametric method is proposed by Barnich\cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). The background model of ViBe consists of pixel samples from the video stream. Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists at least K samples with a distance to itself within a certain range R. 
%PBAS
%
% Ren :这里上下两句话里，我用了一个R，一个R(X)，这两个东西是有关系的，ViBe里面要看距离是不是小于R, 下面这个论文是看距离是不是小于R(X),也就是说每个像素点位置，这个R是不一样的。
%
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold R(x), which depended on the pixel position and a background dynamics metric.

%提出其他方法的问题，指出他们的缺陷
Unfortunately,
the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
%
But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
%
% However, The assumption that pixels are independent to their spatical neighbors is untenable in practice. 
% Ren: 下面这一段，你说不知所云，我的意思是，之前的方法大多只考虑了像素值分布的概率，而不管它们变化过程中的顺序性。
% cqzhao: 不能这么说，实际上专注于distribution的方法不多。
% On the other hand, most pixels-based methods are only concerned with pixels distribution, 
%
%and ignore the order information of input frames by default.
%But there is, in fact, a strong temporal coherence in image sequences that contains abundant hidden clues for the background model. 
%提出我们的改进,我们认为像素在时序上是互相依赖的
% tight interdependence 明明在google scholar里查得到很多用的好不好...
To address this shortcoming, we introduce a novel framework of variation transformation learing, which assume that there is a tight interdependence in pixel's historical observations.
%所以我们把像素整合到一起
% In this case在google scholar里也查得到很多啊
In this case, pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
The benefit of bringing together the observations is to ensure the data integrity and preserve the temporal coherence of our training data. And that guarantee us the ability to take advantage of the spatial-temporal context. 
%所以我们方法比基于像素的要好。
Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
%\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
%
%
%
%
%
%
\subsection{region-based approach}
% Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
Region-based approaches consider the similiary between neighboring pixels, which is utilized to refine the pixel-level classification.
%
% Region-based approaches assume that the neighboring pixels have similar intensities. Hence the spatial correlation is taken into consideration to refine the pixel-level classification.

%(Regularized region-based)
Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
which is derived from expectation maximization theory with the consideration of neighboring pixels while generating the model of the observed scene.
% Spatiotemporal GMM
%
% 妈蛋。居然怀疑我没看过，我看过这篇论文啊，用最小生成树组织了层次化的superpixels,用来做spatial constrains我下面不是提了的吗，只是更抽象一点。。。
In addition, 
Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
%Another GMM based method named Spatiotemporal GMM algorithm was proposed in \cite{2017_TPAMI_GANGWANG}. 
%
%The authors combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
%(Bayesian Modeling)
Moreover, 
Sheikh et al.\ \cite{Sheikh2005Bayesian} introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
%(Robust Foreground Object ICPR2010 Vikas Reddy )
% 这里原文就是用了三层的分类器，不同的方法，一层又一层。
Similarly, in \cite{Reddy2010Robust}, origin images are divided into overlapping blocks. Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
%( Robust Region-Based ICPR)
Hence, Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively. Any foreground region that does not exist in the first foreground map could be recovered from the other one.

%讲其他方法的缺点，不能利用时序相关性，只是在pixel-based方法上添加了空间约束
Unfortunately, most region-based methods are not capable to make use of the temporal coherence, since they are merely adding some spatial constrains to the pixels-based methods. 
%有的方法结合了光流，也算利用了时序相关性
But we also notice that some approaches are involved with optical flow field, which can be viewed as a limited temporal coherence message. 
%但是他们也有几个缺点
However, optical flow methods have shortcommings like the high computation complexity and the sensitivity to illumination changing. 
%最重要的是，他们的时序相关性太有限了。所以对与其他方法，并没有明显的优势。
Moreover, their temporal coherence information is very limited. For each frame, only a few of neighbor frames are taken into account when computing the optical flow.
This could explain why they have no significant improvement compared to their competitors.    
%讲我们方法的不同以及优点
%我们的输入有足量的时序信息。
In the proposed approach, by contrast, we present the pixel matrix, which contains the pixel variation over a longer period of time, to ensure that our DPVTL model has sufficient temporal coherence information to feed.
We also combine the pixel variation with its spatial neighbors to revise our prediction.
%此外，我们借助神经网络可以更有效地计算和捕捉这种时序相关性。
Furthermore, the proposed approach are more powerful in capturing the structural background variation and more efficient in computation due to the application of deep learning.
%
%
%
%
%
% \subsection{learning-based methods}
\subsection{Machine Learning based Methods}
The last category of background subtraction methods apply traditional machine learning and deep learning on different features for the background modeling.

%
%SVM
Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods\cite{Zhang2014Statis}. For example, in \cite{Han2012}, the authors integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel. A pixel wise background model is obtained for each feature in a kernel density framework and a SVM is employed for classification.

%
% Ren: 这个CNN是cascade的结构，就是个层次化预测结果的组合。
Recent years, deep learning starts to flourish in many computer vision fields, significantly improving the state-of-the-art. A novel approach for foreground detection with the use of CNN is proposed by Wang et al.
They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently in dataset2014 with sufficient training data.
%
% Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
%       所以我这里一连提了四个这篇论文训练要采集的patches。 patches 分别来自 平均背景，原始图像，真实图，或者其他算法算出的真实图。
Braham and Droogenbroeck\cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image obtained from temporal median filtering, video frames and groundtruth, or alternatively, segmentation results from other foreground detection methods. Those patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
% Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
A similar approach is presented by M. Babaee et al. \cite{Babaee2017deep}. Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm, which is able to adaptively update the parameters used in the background model. They also utilize spatial-median filtering as the post processing of the network predictions.
%DBMF
%skip结构就是skip结构啊！！就是说前基层的输出在输进下一层的同时，会跳过下一层，输入到更后面去。
In \cite{Yang2018DBMF}, a FCN with the skip architecture is proposed for background modeling. 
The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.

%以上方法的缺点主要在于，他们都是基于静态的图像特征训练的。抛弃了时序相关性。
% cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
Methods in this category are generally based on the static images and static saliency characteristics. 
However, due to the diversity and complexity of nature scenes, it could be rather difficult to analyze the pixel variations for classification. 
%尽管他们用了很好的结构和技巧，但是仍然不能解决这个问题，如何去检测运动，而不是把潜在的运动物体全标记出来。
Even though they have made a lot of progress with optimized network architechtures, it is still an unsolved problem that how to learn the patterns of motion rather than mark out all the possible moving objects.
%我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
% cqzhao: 怎么就是一个输入不同呢？吹的太低的，给我拔高！
Different with their methods, our network is trained to learn the patterns of pixel variations and transform them into a new space for classification.
% 我们的输入XXX
The input of our network is not the origin images or patches. Instead, we regard the pixel variation as a whole for the network training to preseve the temporal coherence between the pixels' historical observations.
%因为我们的方法是基于variation transformation建模的，所以我们的模型在时序建模上有更大的潜力。
% cqzhao: 我们的方法是variation transformation，只是相比他们时许好点而已，不是说我们就只是个时序，吹的不够，拔高！
Now, since the proposed approach is based on the variation transformation, our DPVTL model has more potential in time series modeling on each pixel position.
%此外，我们还将pixel variation 与其空间上的近邻连接起来，从而利用空间上下文信息。
% cqzhao: 这句逻辑有点混乱，我感觉连不上。
In addition, we also concatenate the pixel variation with its spatial neighbors to take advantage of the spatial context. 
%因为我们的网络没有借助于其他传统的背景建模方法，所以取得的效果应该归功于Variation Transformation 框架。
% cqzhao: 你说我们的网络结构简单干嘛》不是不打自招？？？往死里吹，！！！
Our DPVTL model is implemented without any assistance from other tradition background modeling methods, hence the reliable performance owing to the framework of variation transformation.

@@

%variation transformation 介绍。
In this paper, a novel framework of pixel variation transformation are proposed. %用framework代替method?
Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. 
Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
In the specific implementation, we trained a FCN to learn a transformation for the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in \reffig{variation_chart}. 
After thresholding, we can easily get the labels of each observation. 
%方法的好处是
The benefits from variation transformation are evident and clearly seen. 
It is hard to distinguish a foreground observation when its value are similar to the background ones. 
However, classification on the transformed variation is much convenient and intuitive, due to the advantage of temporal information. 
With the aid of deep learning method, the proposed approach can be effectively implemented.

@@

%me
\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
\label{sec4}
In this section, we introduce the proposed approach that consists of a novel FCN network for foreground detection. 
We explain the details of the procedures of pixel matrixes, which is a specific form of the pixel variation, and the architecture of our network.

The complete system is illustrated in \reffig{flow_chart}. 
Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size matrixes and feed them into the network with its spatial neighbors. 
After reassembling the matrixes into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure*}[!t] % FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{Fully convolutional network can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
    \label{flow_chart}
\end{figure*}

@@

% 第三步变成矩阵形式，解释为什么要把variation 变形
Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
However, vectors are not appropriate for the network training and learning. 
Besides, we also hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
Thus we reshape the variations into pixel matrixes as the input of our network. 
A sample of pixel matrix $H^m$ is like this:
\begin{equation}
H^m=P^m_{i+j*d}=\begin{bmatrix}
 P^m_1& P^m_2  &\dots  &P^m_d \\ 
\vdots &  &  &\vdots \\ 
 P^m_{1+(d-1)d}& \dots & \dots & P^m_n
\end{bmatrix},\quad d^2=n,
\end{equation}

Pixel variations are put into the $d\times d$ matrix according to the order of top to bottom and left to right. 
The parameter $i$ and $j$ represent the column and row respectively. 
And the parameter $n$ is the total frame length of a variation, as the same as the observation sequences. 
To put it from another way, the pixel matrix is just a specific form of the pixel variation. 
Although the observation matrix and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation. 
Since the pixel sequences are extracted from individual pixels, a large number of pixel matrixes may be extracted from only a single image stack.

>>>>

% \authorrunning{Lecture Notes in Computer Science: Chongqing University}

@@

\begin{abstract}
%
% 运动检测的已有方法主要关注于像素值的变化。
Previous approaches to foreground detection generally analyze the variation of pixel observations.
% 本文中，我们分析了像素的变动，并提出了DPVTL方法。
% In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
In this paper, we analyze the variation of pixel observations, and a novel foreground detection method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
% 一个FCN被用来寻求一个变换，可以使变换过后的像素值线性可分。
A fully convolutional network(FCN) is applied to find a transformation of pixel variations, which guarantees the linear separability of transformed pixels.
% 具体来说，我们用一段像素观测值表示pixel variation,并用作网络的输入。 
In particular,
the pixel variation is represented by the sequence of pixel observations and used as the input of the FCN.
% 接下来，FCN学习像素变动的模式，并接上一个线性分类器给像素打标签。
Then, the FCN is trained to learn the pattern of pixel variations for the transformation, followed by a liner classifier for labeling the pixels as foreground or background.
%    
% XXX 这句话还是有点问题
% 这句话我也没看懂。。。
Benefied from the ingenious utilization of deep learning network leading by our clear cognition of essence about foreground detection problem,
the proposed approach adaptively generate superior peroformances in diversly complex scenes.
%
Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
%
\end{abstract}

@@

%具体介绍
% XXX 一句话，换一行！！！
% In this paper, we propose a novel Deep Variation Transformation Learning (DVTL) model for foreground detection in diversely natural scenes. 
In the DVTL model, 
the sequence of pixel observations is used to represent the variation and input into the network for learning,
which encode both the intensity distribution and sequential information.
%
Then, a Fully Convolutional Network (FCN)\ \cite{Shelhamer2017fcn} is applied to learn the patterns of the pixel variation and find a transformation which guarantees the linear separability of transformed pixel variation generated by mapping in a new space.
%
In particular,
we take advantage of the strong learning ability of FCN to learn an end-to-end representation of the pixel variation in a new space where they can be easily classified to background and foreground.
%
Benefited from the strong learning ability of FCN,
proposed approach works well in diversely complex scenes adaptively.
%
%Moreover,
%since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack, which promises that sufficient training data can be obtained with limited groundtruth.
% 
% 
% 
% \todo{This paragraph is too short! provide comprehensive details of our work!}
% % The final prediction can be obtained by thresholding of the transformed variation. 
% %Our contributions can be summarized as follows:
% The contridbutions of proposed approach is shown as follows:
% \begin{itemize}
% \item We proposed the pixel observation patch to describe the pixel variation, which encode both the intensity distribution and sequential information over time.
%     The observation patch is obtained by reshaping the vector of a pixel's historical observations, subtracted from the image stacks. 
% \item We propose a deep neural network for variation transformation. 
%     Our FCN network is trained to learn the pixel variation and generate a new representation in a new feature space. 
% \end{itemize}
% 
%文章结构

%The outline of this paper is as follows: In Section II, we give a brief discussion about the early and recent relevant works. 
% XXX 不会用引用可以问我或者曲师兄。
The rest part of this paper is organized as follows: In \refsec{sec2}, we give a brief discussion about the early and recent relevant works. 
%
The details of the variation transformation are presented in \refsec{sec3}. The proposed fully convolutional network is illustrated in \refsec{sec4}, followed by experiments and result comparison in \refsec{sec5} and conclude the paper in \refsec{sec6}. 
% \todo{please revise this part by using command refsec}

\section{Related Work}
\label{sec2}
Over the last few decades, a huge number of background modeling methods have been proposed,
which are broadly categorized into pixel-based, region-based and learning-based methods.
\subsection{pixel-based methods}
% Ren:重新解释了pixel based methods
Pixel-based methods usually assume the independence between neighboring pxiels,
and utilize the low-level features, such as color or gradients for background subtraction.

%GMM 
% cqzhao: 我没有看到过over time，如果你在trans或者顶会(ICCV,CVPR,ECCV)里找到了论文原话，那你可以用哦。
In particular, the Gaussian Mixture Model (GMM) proposed by Stauffer et al.\ \cite{Stauffer1999} is the most popular approach among pixels-based methods.
% 注意英语和汉语的表达习惯
It utilizes a mixture of weighted Gaussians to model the probability distribution of each pixel in time sequence.
Pixels are considered as background if there exists a Gaussian function includes their values with sufficient evidence. 
%GMM+i
Moreover,
Zivkovic et al.\ \cite{Zivkovic2004} improve the GMM method with the utilization of recursive equation
to automatically update the parameters and adjust the needed number of components of mixture for each pixel. 
%
%codebook
Hence, Kim et al.\cite{Kim2005} present the codebook method, which records the sampling background values to codewords for each pixel position.
The incoming pixels are compared with these codewords to see if their distances lies within a certain bound. 
%KDE
A non-parametric background model is proposed by Elgammal et al. \cite{Elgammal2000Non}. 
Authors assume that each background pixel is drawn from a probability distribution function, which is estimated with Kernel Density Estimation(KDE). 
%Vibe
Another non-parametric method is proposed by Barnich et al. \cite{Barnich2011_2011_TIP}, called the Visual Background Extractor (ViBe). The background model of ViBe consists of pixel samples from the video stream. Each pixel in the current frame is compared with sampling pixels from the corresponding background model and labelled as the foreground when there exists sufficient samples with a distance to itself within a certain range. 
%PBAS
To adaptively update the parameters, Hofmann et al.\cite{Hofmann2012Background} improve the ViBe by presenting an adaptive threshold, which depended on the pixel position and a background dynamics metric.

%提出其他方法的问题，指出他们的缺陷
Unfortunately,
the pixel-based methods ignore the spatial-temporal information due to their assumption of independence between pixels.
But there is, in fact, a strong coherence in image sequences that contains abundant hidden clues for the background model. 
%
%提出我们的改进,我们认为像素在时序上是互相依赖的
% tight interdependence 明明在google scholar里查得到很多用的好不好...
% To address this shortcoming, 在一篇2018的CVPR的摘要里有啊
% “High Quality Estimation of Multiple Intermediate Frames for Video Interpolation”
To address this shortcoming, we introduce a framework of variation transformation learing, where pixel's historical observations are embedded in a piece of pixel variation and sorted in chronological order as a whole to enter our DPVTL model.
%这样的优点在于保留了数据的完整性，保留了数据的时序相关性。
Bringing together the historical observations ensures the data integrity and preserves the temporal coherence of our training data. 
Moreover, 
the novel framework is more capable of learning the patterns of pixel variation and exploiting the spatial-temporal context, compared to those classifiers for individual observations. 
%所以我们方法比基于像素的要好。
%Hence we demonstrate a comparatively better performance in modelling some challenging scenes, like illumination changing and intermittent object motion.
%\todo{you should discuss the difference between the proposed approach and pixel-based method. What is your advantage compared with these previous work? Why they failed and why our method work?}
%
%
%
%
%
%
\subsection{region-based approach}
% Ren: 好的好的，不乱吹了，我看过有说have similar values的。。。。
Region-based approaches consider the similiary between neighboring pixels, which is utilized to refine the pixel-level classification.
%

%(Regularized region-based)
Varadarajan et al.\ \cite{2015_PR_Varadarajan20153488} proposed a region-based GMM model,
which is derived from expectation maximization theory with the consideration of neighboring pixels.
% Spatiotemporal GMM
In addition, 
Chen et al. \cite{2017_TPAMI_GANGWANG} combine the GMM with constrains of temporal and spatial information from the optical flow and hierarchical superpixels.
%(Bayesian Modeling)
Moreover, 
Sheikh et al.\ \cite{Sheikh2005Bayesian} introduce a framework based on the Markov Random Field modeling with Maximum A Posteriori 
probability (MAP-MRF) estimation, which incorporate the pixel location into background and foreground KDEs for the detection based on spatial context.
%(Robust Foreground Object ICPR2010 Vikas Reddy )
% 这里原文就是用了三层的分类器，不同的方法，一层又一层。
Similarly, in \cite{Reddy2010Robust}, origin images are divided into overlapping blocks. Each block is sequentially processed by an adaptive multi-stage classifier, which consists of a likelihood evaluation, an illumination invariant measure and a temporal correlation check.
%( Robust Region-Based ICPR)
Hence, Izadi et al.\cite{Izadi2008Robust} present a robust region-based approach, which generates a pair of foreground maps based on gradient and color respectively. Any foreground region that does not exist in the first foreground map could be recovered from the other one.

In this paper, we accept the assumption that neighboring blocks of background pixels should follow similar variations over time, and combine the pixel variation with its spatial neighbors to revise our prediction. 
Due to the application of deep learning, the proposed approach is more powerful in capturing the structural background variation and achieves significant improvement compared to its competitors.
%
%
%
% \subsection{learning-based methods}
\subsection{Machine Learning based Methods}
The last category of background subtraction methods apply traditional machine learning and deep learning for the background modeling.

%
%SVM
Traditional machine learning methods are commonly involved with support vector machines (SVM) and Bayesian methods\cite{Zhang2014Statis}. For example, Han et al. \cite{Han2012} integrate gradient, color, and Haar-like features to address the spatiotemporal variations for each pixel. Their background model is obtained for each feature in a kernel density framework and a SVM is employed for classification.

%
Recent years, deep learning methods start to flourish in many computer vision fields, and significantly improve the state-of-the-art in experiments. A novel approach for foreground detection with the use of CNN is proposed by Wang et al.\cite{wang2016PRL}.
They utilize a CNN with a cascade network architecture for segmentation in foreground detection, which perform excellently with sufficient training data.
%
% Ren: 这里我解释一下，为什么看上去这么冗余。这家伙先自己用中值滤波求了个平均背景，然后把平均背景 patches 跟对应的origin image patches 组合作为网络输入，他训练的groundtruth也可以来自其他比如GMM的分类结果图。
Braham et al. \cite{Braham2016deep} employ a scene-specific CNN, which is trained with corresponding image patches from the background image, video frames and groundtruth. In particular, the background image is obtained by temporal median filtering, and the groundtruth be replaced with segmentation results from other foreground detection methods. Patches are extracted around a pixel, then they are feed into the network and compared with a threshold.
% Ren: 下面这个家伙做法跟上面太类似了，就是背景图像不用中值滤波，而是用其他牛一点的方法去获取。MD
A similar approach is presented by M. Babaee et al. \cite{Babaee2017deep}. Their background images combine the segmentation mask from SuBSENSE\cite{St-Charles2015SuBSENSE} algorithm and the output of Flux Tensor algorithm \cite{Wang2014FTSG}, which is able to adaptively update the parameters used in the background model. They also utilize spatial-median filtering as the post processing of the network predictions.
%DBMF
In \cite{Yang2018DBMF}, a fully convolutional network with the skip architecture is proposed for background modeling. 
The authors also proposed a temporal approach to sample training images from the given video, thus providing the background model with limited temporal information.

% cqzhao: 瞎说啥？？？SVM那个就是连续的几帧啊！他们的问题在于， 自然界太复杂，variation太多元，直接分析variation分析不出来，我们学到了variation的pattern，然后转换！
Methods in this category have made a lot of progress, especially deep learning based approaches with optimized network architechtures. 
However, due to the diversity and complexity of nature scenes, it is still difficult to analyze the pixel variations for classification. 
%我们的不同在于，我们的网络是训练去学习像素变动，并转换到新的空间去进行分类。
Different with their methods, we focus on creating a transformation, which guarantees the linear sparability of pixel variations in the mapping space, rather than building classifiers for individual observations.
%
Besides, our network is trained to learn the patterns of pixel variations, which promises a better performance in time series modeling on temporal coherence.
%
Moreover, our DPVTL model is implemented without any assistance from other tradition background modeling methods, hence the reliable performance owing to the noval framework of variation transformation.

@@

%variation transformation 介绍。
In this paper, a novel framework of pixel variation transformation are proposed. %用framework代替method?
Pixel observations are no longer considered independent of each other but regarded as a whole, which we call the pixel variation. 
Consequently, the classification of pixels can be viewed as a transformation of pixel variations, from the observation sequences to the prediction sequences. 
In the specific implementation, we trained a FCN to learn a transformation of the pixel variations by mapping them into a new space where it is close to the groundtruth, just like the green line in \reffig{variation_chart}. 
After thresholding, we can easily get the labels of each observation. 
%方法的好处是
The benefits from variation transformation are evident and clearly seen. 
It is hard to distinguish a foreground observation when its value are similar to the background ones. 
However, classification on the transformed variation is much convenient and intuitive, due to the advantage of temporal information. 
With the aid of deep learning method, the proposed approach can be effectively implemented.

@@

%me
\section{foreground detection VIA DEEP VARIATION TRANSFORMATION}
\label{sec4}
In this section, we introduce the proposed approach that consists of a novel FCN network for foreground detection. 
We explain the details of the procedures of pixel patches, which is a specific form of the pixel variation, and the architecture of our network.

The complete system is illustrated in \reffig{flow_chart}. 
Firstly, we temporally sample the input and ground truth images to generalize the pixel variations, and reshape them into fixed-size patches and feed them into the network with its spatial neighbors. 
After reassembling the patches into the complete output frame, it is post-processed, yielding the final segmentation of the respective video frame.
\begin{figure*}[!t] % FIGURE: figure/fig1 
\centering
\includegraphics[width=\textwidth]{figure/fig2}
\DeclareGraphicsExtensions.
    \caption{Fully convolutional network can efficiently learn to make dense predictions for per-pixel tasks like semantic segmentation.}
    \label{flow_chart}
\end{figure*}

@@

% 第三步变成矩阵形式，解释为什么要把variation 变形
Our intention is to provide an end-to-end transformation of pixel variations, based on the strong learning ability of FCNs. 
However, vectors are not appropriate for the network training and learning. 
Besides, we also hope the pixel observations can be interacted with their further compatriots in temporal sequence. 
Thus we reshape the variations into pixel patches as the input of our network. 
A sample of pixel patch $H^m$ is like this:
\begin{equation}
H^m=P^m_{i+j*d}=\begin{bmatrix}
 P^m_1& P^m_2  &\dots  &P^m_d \\ 
\vdots &  &  &\vdots \\ 
 P^m_{1+(d-1)d}& \dots & \dots & P^m_n
\end{bmatrix},\quad d^2=n,
\end{equation}

Pixel variations are put into the $d\times d$ patch according to the order of top to bottom and left to right. 
The parameter $i$ and $j$ represent the column and row respectively. 
And the parameter $n$ is the total frame length of a variation, as the same as the observation sequences. 
To put it from another way, the pixel patch is just a specific form of the pixel variation. 
Although the observation patch and the observation sequence belong to different forms of the pixel variation, they consist of the same components, and share the common temporal information from the pixel variation. 
Since the pixel sequences are extracted from individual pixels, a large number of pixel patches may be extracted from only a single image stack.
